The Concurrent Calculi Formalisation Benchmark\\{\normalsize(Talk Proposal)

### 2023-07-10 extended-abstract/extended-abstract.tex
Change "extended abstract" to "talk proposal".

\title{The Concurrent Calculi Formalisation Benchmark\\{\normalsize(Extended Abstract)}}
\def\titlerunning{The Concurrent Calculi Formalisation Benchmark (Extended Abstract)}

>>>>

\title{The Concurrent Calculi Formalisation Benchmark\\{\normalsize(Talk Proposal)}}
\def\titlerunning{The Concurrent Calculi Formalisation Benchmark (Talk Proposal)}
